% Prepared by Calvin Kent
%
% Assignment Template v19.02
%
%%% 20xx0x/MATHxxx/Crowdmark/Ax
%
\documentclass[12pt]{article} %
\usepackage{CKpreamble}
\usepackage{CKassignment}
\usepackage{tkz-euclide}
\usepackage{physunits}
\usepackage{physics}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{upgreek}
\usepackage{xcolor}
\usepackage{euscript}
\usepackage{tasks}
\usepackage{tkz-euclide}


\usepackage[misc]{ifsym}


%%Title
\title{Julius Caeser - Act 2 Quiz}
\date{April, 2022}

%%% Maths and science packages

\usepackage{amsmath,amsthm,amssymb}
\usepackage{pgfplots}
	\usetikzlibrary{
		calc,
		patterns,
		positioning
	}
	\pgfplotsset{
		compat=1.16,
		samples=200,
		clip=false,
		my axis style/.style={
			axis x line=middle,
			axis y line=middle,
			legend pos=outer north east,
			axis line style={
				->,
			},
			legend style={
				font=\footnotesize
			},
			label style={
				font=\footnotesize
			},
			tick label style={
				font=\footnotesize
			},
			xlabel style={
				at={
					(ticklabel* cs:1)
				},
				anchor=west,
				font=\footnotesize,
			},
			ylabel style={
				at={
					(ticklabel* cs:1)
				},
				anchor=west,
				font=\footnotesize,
			},
			xlabel= $x$,
			ylabel=$\vec d (\m \tx{[East]})$
		},
	}
	\tikzset{
		>=stealth
	}

%%% Tables and figures packages

\usepackage{float}
\usepackage{caption}
	\captionsetup{
		format=plain,
		labelfont=bf,
		font=small,
		justification=centering
	}

%%% Numbers and sets

\newcommand{\E}{\mathrm{e}}

\newcommand{\tx}[1]{\text{#1}}

\begin{document}
    \pagenumbering{arabic}
    % Start of class settings ...
    \renewcommand*{\coursecode}{MCR3U Quiz} % Quiz Title
    \renewcommand*{\assgnnumber}{2} % Quiz number
    \renewcommand*{\submdate}{January, 2022} % renew the date
    \renewcommand*{\studentfname}{\textbf{Name:}} % Student first name
    \renewcommand*{\studentlname}{} % Student last name
    %\renewcommand*{\studentnum}{SNumber} % Student number

    \renewcommand\qedsymbol{$\blacksquare$}
    \setfigpath
    % End of class settings
    \pagestyle{crowdmark}
    \newgeometry{left=18mm, right=18mm, top=22mm, bottom=22mm} % page is set to default values
    \fancyhfoffset[L,O]{0pt} % header orientation fixed
    % End of class settings
    %%% Note to user:
    % CTRL + F <CHANGE ME:> (without the angular brackets) in CKpreamble to specify graphics paths accordingly.
    % The command \circled[]{} accepts one optional and one mandatory argument.
    % Optional argument is for the size of the circle and mandatory argument is for its contents.
    % \circled{A} produces circled A, with size drawn for letter A. \circled[TT]{A} produces circled A with size drawn for TT.
    % https://github.com/CalvinKent/My-LaTeX
    %%%
    % Crowdmark assignment start


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%                  PROBLEM IDEAS                  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%                   ----------------------------------------                                %%%%%%%%

    % --> Do a hard tangent line problem

	\maketitle
	\section{Preamble}
    This is a quiz covering all of Act 2 from \textit{Julius Caeser}.
	\section{Allowed Aids}
  This is a closed book quiz, nothing is allowed.
	\section{Name and Date:}
	Print your name and todays date below;

  \vspace*{0.4cm}

	\begin{center}
	\noindent\begin{tabular}{ll}
		\makebox[3in]{\hrulefill} & \makebox[3in]{\hrulefill}\\
		Name & Date\\[8ex]% adds space between the two sets of signatures
	\end{tabular}
	\end{center}
	\newpage


\begin{qstn}
  For each of the following, identify the \textbf{speaker} and provide a \textbf{brief explanation} for what was said.

  \begin{enumerate}
    \item
        \begin{verse}
          But 'tis a common proof \\
          That lowliness is young ambition' ladder,\\
          Whereto the climber upward turns his face; \\
          But when he once attains the upmost round,\\
          He then unto the ladder turns his back, \\
          Looks in the clouds, scorning the base degrees \\
          By which he did ascend.
        \end{verse}
       \vspace*{7cm}
    \item
       \begin{verse}
         Decius, well urged. I think it is not meet \\
         Mark Antony, so well beloved of Caeser,\\
         Should outlive Caeser, we shall find him \\
         A shrewd contiver, and you know, his means;...\\
         Let Antony and Caeser fall together.
       \end{verse}
          \newpage

    \item
        \begin{verse}
          No, not an oath. If not the face of men, \\
          The sufferance of our souls, the time's abuse - \\
          If these motives weak, break off bedtimes, \\
          And every man hence to his idle bed. \\
          So let high-sighted tryanny range on \\
          Till each man drop by lottery. But if these \\
          (As I am sure they do) bears fire enough...
        \end{verse}
       \vspace*{11cm}

    \item
        \begin{verse}
          Thou, like an exorcist, has conjured up \\
          My mortified spirit. Now bid me run
        \end{verse}
          \newpage
    \item
        \begin{verse}
          Alas, my lord\\
          Your wisdom is consumed in confidence. \\
          Do not go forth today. Call it may fear
        \end{verse}

  \end{enumerate}


\end{qstn}

\vspace*{6cm}


\begin{qstn}
  Explain the meaning of the following terms:
  \begin{enumerate}
    \item \textbf{Taper}:

       \vspace*{3cm}

    \item \textbf{Closet}:
       \vspace*{3cm}

    \item \textbf{Exhalations:}
       \vspace*{3cm}

    \item \textbf{Time's abuse}:
       \vspace*{3cm}

  \end{enumerate}



\end{qstn}


\begin{qstn}
  Answer the following question's completely.
  \begin{enumerate}
    \item How did Brutus react to the following letter:
        \begin{verse}
          Brutus, thou sleep'st; awake and see thyslef.\\
          Shall Rome, \&c. Speak, strike, redress. \\
          Brutus, thou sleep'st; awake.
        \end{verse}
\vspace*{6cm}

    \item Why did the priests tell Caeser to remain at home?
\vspace*{4cm}

    \item Why does Caeser decide not to go to the Senate House? How does Decius convince Caeser that he should go?
  \end{enumerate}

\end{qstn}































\end{document}
