% Prepared by Calvin Kent
%
% Assignment Template v19.02
%
%%% 20xx0x/MATHxxx/Crowdmark/Ax
%
\documentclass[12pt]{article} %
\usepackage{CKpreamble}
\usepackage{CKassignment}
\usepackage{tkz-euclide}
\usepackage{physunits}
\usepackage{physics}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{upgreek}
\usepackage{xcolor}
\usepackage{euscript}
\usepackage{tasks}
\usepackage{tkz-euclide}


\usepackage[misc]{ifsym}


%%Title
\title{Grammar Quiz 1}
\date{March, 2022}

%%% Maths and science packages

\usepackage{amsmath,amsthm,amssymb}
\usepackage{pgfplots}
	\usetikzlibrary{
		calc,
		patterns,
		positioning
	}
	\pgfplotsset{
		compat=1.16,
		samples=200,
		clip=false,
		my axis style/.style={
			axis x line=middle,
			axis y line=middle,
			legend pos=outer north east,
			axis line style={
				->,
			},
			legend style={
				font=\footnotesize
			},
			label style={
				font=\footnotesize
			},
			tick label style={
				font=\footnotesize
			},
			xlabel style={
				at={
					(ticklabel* cs:1)
				},
				anchor=west,
				font=\footnotesize,
			},
			ylabel style={
				at={
					(ticklabel* cs:1)
				},
				anchor=west,
				font=\footnotesize,
			},
			xlabel= $x$,
			ylabel=$\vec d (\m \tx{[East]})$
		},
	}
	\tikzset{
		>=stealth
	}

%%% Tables and figures packages

\usepackage{float}
\usepackage{caption}
	\captionsetup{
		format=plain,
		labelfont=bf,
		font=small,
		justification=centering
	}
	
%%% Numbers and sets

\newcommand{\E}{\mathrm{e}}

\newcommand{\tx}[1]{\text{#1}}

\begin{document}
    \pagenumbering{arabic}
    % Start of class settings ...
    \renewcommand*{\coursecode}{MCR3U Quiz} % Quiz Title
    \renewcommand*{\assgnnumber}{2} % Quiz number
    \renewcommand*{\submdate}{January, 2022} % renew the date
    \renewcommand*{\studentfname}{\textbf{Name:}} % Student first name
    \renewcommand*{\studentlname}{} % Student last name
    %\renewcommand*{\studentnum}{SNumber} % Student number

    \renewcommand\qedsymbol{$\blacksquare$}
    \setfigpath
    % End of class settings 
    \pagestyle{crowdmark}
    \newgeometry{left=18mm, right=18mm, top=22mm, bottom=22mm} % page is set to default values
    \fancyhfoffset[L,O]{0pt} % header orientation fixed
    % End of class settings
    %%% Note to user:
    % CTRL + F <CHANGE ME:> (without the angular brackets) in CKpreamble to specify graphics paths accordingly.
    % The command \circled[]{} accepts one optional and one mandatory argument.
    % Optional argument is for the size of the circle and mandatory argument is for its contents.
    % \circled{A} produces circled A, with size drawn for letter A. \circled[TT]{A} produces circled A with size drawn for TT.
    % https://github.com/CalvinKent/My-LaTeX
    %%%
    % Crowdmark assignment start


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%                  PROBLEM IDEAS                  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%                   ----------------------------------------                                %%%%%%%%

    % --> Do a hard tangent line problem

	\maketitle
	\section{Preamble}
  This is a grammar quiz covering what we have learned in lecture so far (Up to lesson 4).
	\section{Allowed Aids}
  This is a closed book quiz, nothing is allowed.
	\section{Name and Date:}
	Print your name and todays date below;

  \vspace*{0.4cm}

	\begin{center}
	\noindent\begin{tabular}{ll}
		\makebox[3in]{\hrulefill} & \makebox[3in]{\hrulefill}\\
		Name & Date\\[8ex]% adds space between the two sets of signatures
	\end{tabular}
	\end{center}
	\newpage


\begin{qstn}[1]
  For each of the following quotes, insert a comma where you feel is appropriate. If you feel like the quote
  is correct as is, then leave it. \textbf{Provide a brief explanation} for your corrections.

  \begin{enumerate}
    \item "While you were wrestling Maalik I was slapping Qaasim."
      \vspace*{4cm}

    \item "For our grammar lesson today we will be taking a look at how to
      correctly implement the ! punctuation mark."
      \vspace*{4cm}
      
    \item "Br.Abdullah you are an old man period."
      \vspace*{4cm}

    \item "I have a fruitful passion towards boxing my students and my siblings."
      \vspace*{4cm}

  \end{enumerate}

  
\end{qstn}


\begin{qstn}[2]
  For each of the following quotes, correct the adjective or adverb where you feel is appropriate. If you feel like the quote
  is correct as is, then leave it. \textbf{Provide a brief explanation} for your corrections.
  
  \begin{enumerate}
    \item "His parents were real mad that he used the washroom in his pants."
      \vspace*{4cm}

    \item "Sometimes thriller movies end bad".
      \vspace*{4cm}
      
    \item "It felt well to hit Maalik."
      \vspace*{4cm}

    \item "My grandfather looks good for someone his age"
      \vspace*{4cm}

  \end{enumerate}
  
\end{qstn}

\begin{qstn}[3]
  For each of the following quotes, ensure that pronoun agreement is correct. If you feel like the quote
  is correct as is, then leave it. \textbf{Provide a brief explanation} for your corrections.

  \begin{enumerate}
    \item "Neither of my classmates are liking this new teacher, his beard is far too ugly"
      \vspace*{4cm}

    \item "Anyone in the following age group is encouraged to share their opinion".
      \vspace*{4cm}
      
    \item "Several of the students felt like their teacher had diarrhea."
      \vspace*{4cm}


  \end{enumerate}
\end{qstn}






























\end{document}
