% Prepared by Calvin Kent
%
% Assignment Template v19.02
%
%%% 20xx0x/MATHxxx/Crowdmark/Ax
%
\documentclass[12pt]{article} %
\usepackage{amsthm}
\usepackage{CKpreamble}
\usepackage{CKassignment}
\usepackage{dirtytalk}
\usepackage{csquotes}
\usepackage{dirtytalk}
\usepackage{mdframed}
\usepackage{euscript}
\usepackage{tikz}
\usepackage{pgfplots}

%
\begin{document}
	\pagenumbering{arabic}
	% Start of class settings ...
	\renewcommand*{\coursecode}{MATH 235} % renew course code
	\renewcommand*{\assgnnumber}{Assignment 1} % renew assignment number
	\renewcommand*{\submdate}{September 14, 2021} % renew the date
	\renewcommand*{\studentfname}{Abdullah} % Student first name
	\renewcommand*{\studentlname}{Zubair} % Student last name
    \renewcommand*{\proofname}{Proof:}
	% \renewcommand*{\studentnum}{20836288} % Student number

	\renewcommand\qedsymbol{$\blacksquare$}
	\setfigpath
	% End of class settings	
	% \pagestyle{crowdmark}
	\newgeometry{left=18mm, right=18mm, top=22mm, bottom=22mm} % page is set to default values
	\fancyhfoffset[L,O]{0pt} % header orientation fixed
	% End of class settings
	%%% Note to user:
	% CTRL + F <CHANGE ME:> (without the angular brackets) in CKpreamble to specify graphics paths accordingly.
	% The command \circled[]{} accepts one optional and one mandatory argument.
	% Optional argument is for the size of the circle and mandatory argument is for its contents.
	% \circled{A} produces circled A, with size drawn for letter A. \circled[TT]{A} produces circled A with size drawn for TT.
	% https://github.com/CalvinKent/My-LaTeX
	%%%

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%                        CUSTOM MACRO VIM-TEX                                                      (Word Wrap->
	%%       call IMAP('NOM', '\nomenclature{}', 'tex')               

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	% Crowdmark assignment start
	% qnumber, qname, points


\begin{center}
  \textbf{\underline{\Huge{MLA Citation - Example List}}}
\end{center}


\subsection*{Author}
\begin{enumerate}
  \item Bhabha, Homi K. \textit{The Location of Culture}. Routledge, 1994.
\end{enumerate}


\subsection*{Title Of Source}
\begin{enumerate}
  \item Henley, Patricia. \textit{The Hummingbird House}. MacMurray, 1999.
  \item Lundman, Susan. "How to Make Vegetarian Chili." eHow, (WEBSITE URL)
  \item Bagchi, Alaknanda. "Conflicting Nationalisms: The Voice of the Subaltern in Mahasweta Devi's Bashai Tudu." Tulsa Studies in Women's Literature, vol. 15, no. 1, 1996, pp. 41-50.
\end{enumerate}


\subsection*{TITLE OF CONTAINER}
\begin{enumerate}
  \item Kincaid, Jamaica. "Girl." \textit{The Vintage Book of Contemporary American Short Stories}, edited by Tobias Wolff,
  Vintage, 1994, pp. 306-07.
\end{enumerate}


\subsection*{Other Contributions}

\begin{enumerate}
  \item Foucault, Michel. \textit{Madness and Civilization: A History of Insanity in the Age of Reason}. Translated by Richard Howard,
  Vintage-Random House, 1988.
  \item Woolf, Virginia. \textit{Jacob’s Room}. Annotated and with an introduction by Vara Neverow, Harcourt, Inc., 2008.
  \item 
\end{enumerate}

\subsection*{Version}

\begin{enumerate}
  \item \textit{The Bible}. Authorized King James Version, Oxford UP, 1998.
\end{enumerate}


\subsection*{Number}
\begin{enumerate}
  \item Quintilian. \textit{Institutio Oratoria}. Translated by H. E. Butler, vol. 2, Loeb-Harvard UP, 1980.
\end{enumerate}


\subsection*{Publisher}
\begin{enumerate}
  \item \textit{Women's Health: Problems of the Digestive System}. American College of Obstetricians and Gynecologists, 2006.
  \item Daniels, Greg and Michael Schur, creators. \textit{Parks and Recreation}. Deedle-Dee Productions and Universal Media Studios, 2015.
\end{enumerate}


\subsection*{Publication Date}
\begin{enumerate}
  \item “Hush.” \textit{Buffy the Vampire Slayer}, created by Joss Whedon, performance by Sarah Michelle Gellar, season 4, Mutant Enemy, 1999.
\end{enumerate}

\subsection*{Location}
\begin{enumerate}
  \item \textbf{(Essay)} Adiche, Chimamanda Ngozi. “On Monday of Last Week.”\textit{ The Thing around Your Neck}, Alfred A. Knopf, 2009, pp. 74-94.
  \item \textbf{(Physical Object)} Matisse, Henri. \textit{The Swimming Pool}. 1952, Museum of Modern Art, New York.
\end{enumerate}

\vspace*{15cm}



\textit{MLA Formatting and Style guide}, Purdue Online Writing Lab, Purdue University.\\

\end{document}































































